Data Management Plan

### 2021-11-30 application/dataManagementPlan_longJR.tex
Fixed typos

Team responsibilities: Dr.~Lopes (Bonsai related software development, software
releases, organization of Bonsai workshops and co-supervision of research
software engineer), Dr.~Rapela (machine learning software development, testing
maching learning functionality with behavioral and neural recordings and
co-supervision of research software engineer), Prof.~Sahani (supervision on
maching learning and neural data analysis), Prof.~Mrsic-Flogel (superivision on
neuroscience topics and communication with the steering committee).

@@

    \item[disfunctional machine learning functionality] in Section 2.3 of the
        Case for Support document (Figure 2, green box) we proposed to
        integrate existing machine learning methods into the Bonsai ecsosystem.
        It could be that some of these methods do not work as reliably as
        needed for our resource. In such a case we will use another existing
        methods with similar functionality.  This risk should not be a major
        problem for the proposed project, since most of the machine learning
        methods we proposed to incorporate into Bonsai have been
        developed by us, or we are substantial experienced using them.

    \item[lack of interest from Bonsai users] we will minimize the probability
        of this problem by demonstrating broadly among Bonsai users the unique
        capabilities of the new machine learning functionality.  We don't think
        this would be a serious problem, since Bonsai users have reapeatly
        asked the addition of machine learning functionality to Bonsai (Section
        3 Community demand, Case for Support), and because the functionality we
        proposed to add to Bonsai (Section~2.3, Case for Support) is of large
        interest among experimental-control neurocientists.

    \item[lack of interest from machine-learning methods developers] to reduce
        the probability of this problem we will take three actions. First, we
        will provide machine-learning methods developers and easy-to-use API to
        interface their methods into the Bonsai ecosystem. Second, we will
        demonstrate them the large user exposure that Bonsai offers to
        integrated maching learning functionality. Third, we will organize
        Bonsai workshops for methods developers showcasing machine learning
        methods already integrated into the Bonsai ecosystem and instructing
        them on how to integrate new methods into the Bonsai ecosystem.

@@

Currently Bonsai is a well-known software. A strategy that its author has
used to gain this visiability is to build interoperability with a large number
of open-source source projects for data acquistion. With the addition of the
proposed machine learning functionality, Bonsai will interact with popular
machine learning algorithms, which will confer Bonsai further visibility.

@@

Several factors will contribute to the reusability of new functionality
incorporated into Bonsai. Code implementing this functionality will be
available in Github and Zenodo, under MIT license. Emphasis on standard and
uniform code style, achieved with the help of code review and paired
programming, will generate readable code, easier to read and extend by third
parties. Automated build methods, will simplify code building and encourage
modification by new developers. Test cases with large coverage will motivate
software developers to modify Bonsai, without the risk of introducing
undetected bugs into the software. Carefully designed software, with simple and
clear object interfaces, will simplify the resuse of the proposed software.

>>>>

Team responsibilities: Dr.~Lopes (Bonsai related software development, software
releases, organisation of Bonsai workshops and co-supervision of research
software engineer), Dr.~Rapela (machine learning software development, testing
machine learning functionality with behavioral and neural recordings and
co-supervision of research software engineer), Prof.~Sahani (supervision on
machine learning and neural data analysis), Prof.~Mrsic-Flogel (supervision on
neuroscience topics and communication with the steering committee).

@@

    \item[dysfunctional machine learning functionality] in Section 2.3 of the
        Case for Support document (Figure 2, green box) we proposed to
        integrate existing machine learning methods into the Bonsai ecosystem.
        It could be that some of these methods do not work as reliably as
        needed for our resource. In such a case we will use another existing
        methods with similar functionality.  This risk should not be a major
        problem for the proposed project, since most of the machine learning
        methods we proposed to incorporate into Bonsai have been
        developed by us, or we are substantial experienced using them.

    \item[lack of interest from Bonsai users] we will minimise the probability
        of this problem by demonstrating broadly among Bonsai users the unique
        capabilities of the new machine learning functionality.  We don't think
        this would be a serious problem, since Bonsai users have repeatedly
        asked the addition of machine learning functionality to Bonsai (Section
        3 Community demand, Case for Support), and because the functionality we
        proposed to add to Bonsai (Section~2.3, Case for Support) is of large
        interest among experimental-control neurocientists.

    \item[lack of interest from machine-learning methods developers] to reduce
        the probability of this problem we will take three actions. First, we
        will provide machine-learning methods developers and easy-to-use API to
        interface their methods into the Bonsai ecosystem. Second, we will
        demonstrate them the large user exposure that Bonsai offers to
        integrated machine learning functionality. Third, we will organise
        Bonsai workshops for methods developers showcasing machine learning
        methods already integrated into the Bonsai ecosystem and instructing
        them on how to integrate new methods into the Bonsai ecosystem.

@@

Currently Bonsai is a well-known software. A strategy that its author has
used to gain this visibility is to build interoperability with a large number
of open-source source projects for data acquisition. With the addition of the
proposed machine learning functionality, Bonsai will interact with popular
machine learning algorithms, which will confer Bonsai further visibility.

@@

Several factors will contribute to the reusability of new functionality
incorporated into Bonsai. Code implementing this functionality will be
available in Github and Zenodo, under MIT license. Emphasis on standard and
uniform code style, achieved with the help of code review and paired
programming, will generate readable code, easier to read and extend by third
parties. Automated build methods, will simplify code building and encourage
modification by new developers. Test cases with large coverage will motivate
software developers to modify Bonsai, without the risk of introducing
undetected bugs into the software. Carefully designed software, with simple and
clear object interfaces, will simplify the reuse of the proposed software.
